Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-02 main.tex
work on vector/exterior calculus section; improving (ongoing) the potential operators

\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalit\cye{ies} subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions. 
For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.

@@

\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
\begin{gather*}
    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
\begin{gather*}
    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}}

@@

The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
defined by the formula 
\begin{gather*}
    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
    = 
    \frac{1}{k! l!} 
    % \sum_{ \pi \in S_{k+l}} 
    \sum_{ \pi } 
    \signum(\pi) 
    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
\end{gather*}
for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
The exterior product is bilinear and associative, and satisfies 
\begin{align*}
    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
    \quad 
    \forall u_1 \in \Alt^{k}(V),
    \quad 
    \forall u_2 \in \Alt^{l}(V).
\end{align*}
We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
\begin{align*}
    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
    \quad 
    \forall v_1, v_2, \ldots, v_{k-1} \in V.
\end{align*}

We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
Moreover, this particular setting comes with a canonical basis. 
We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
and introduce the basic $k$-alternators 
\begin{align*}
    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
    \quad 
    \forall \sigma \in \Sigma(k,n). 
\end{align*}
These define a basis of $\Alt^{k}(\bbR^{n})$.
Note that 
$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
\mwl{This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}

@@

We are interested in transformations of Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\begin{align} \label{equation:pullback}
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    := 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\end{align}
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
We cite an explicit transformation estimate~\cite{licht2019smoothed}.

\begin{proposition} \label{proposition:pullbackestimate}
 Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
 Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
 Then 
 \begin{align}\label{math:pullbackestimate}
  \begin{split}
  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
  &\leq 
  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
  .
  \end{split}
 \end{align}
\end{proposition}
\notice{MWL:I have simplified the statement to what is needed later.}

\begin{remark}
    In three dimensions, 
    the calculus of differential forms can be translated into classical vector calculus. 
    This is expressed formally as the commuting diagram 
    \begin{gather*}
    \begin{CD}
        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        @VV{\varpi^{3}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
    \end{CD}
    \cye{\, ,}
    \end{gather*}
    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
    \begin{align*}
     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
     &= 
     \left( u_1, u_2, u_3 \right), 
     \\
     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
     &= 
     \left( u_{23}, - u_{13}, u_{12} \right).   
    \end{align*}
    In two dimensions, 
    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
    To the authors' best knowledge, neither convention is dominant in the literature.
    We summarize the situation in the following commuting diagram: 
    \begin{gather*} 
    \begin{CD}
        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
        \\
        @AA{\varkappa^{0}}A 
        @AA{\varkappa^{1}}A 
        @AA{\varkappa^{2}}A 
        \\
        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
    \end{CD}
    \cye{\,.}
    \end{gather*}
    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism. We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
    The other vertical arrows are the identity. 
    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
\end{remark}

@@

We finally review a few approximation properties. 
Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.

@@

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
\end{proof}

@@

We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
We already know the optimal constants for the gradient operator over convex domains,
and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.

>>>>

\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions. 
For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.

@@

\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
\begin{gather*}
    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
\begin{gather*}
    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}

@@

The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra
(see~Chapter 14 in \cite{lee2012smooth}). 
Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
defined by the formula 
\begin{gather*}
    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
    = 
    \frac{1}{k! l!} 
    % \sum_{ \pi \in S_{k+l}} 
    \sum_{ \pi } 
    \signum(\pi) 
    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
\end{gather*}
for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
The exterior product is bilinear and associative, and satisfies 
\begin{align*}
    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
    \quad 
    \forall u_1 \in \Alt^{k}(V),
    \quad 
    \forall u_2 \in \Alt^{l}(V).
\end{align*}
The interior product is in some sense dual to the exterior product. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define the interior product $v \lrcorner u \in \Alt^{k-1}(V)$ via 
\begin{align*}
    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
    \quad 
    \forall v_1, v_2, \ldots, v_{k-1} \in V.
\end{align*}

We employ the exterior algebra only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
Moreover, this particular setting comes with a canonical basis. 
We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
and introduce the basic $k$-alternators 
\begin{align*}
    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
    \quad 
    \forall \sigma \in \Sigma(k,n). 
\end{align*}
These define a basis of $\Alt^{k}(\bbR^{n})$.
Note that 
$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
\mwl{This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}

@@

We are interested in transformations of Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\begin{align} \label{equation:pullback}
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    := 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\end{align}
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
We cite an explicit transformation estimate~ (see~\cite{licht2019smoothed}) and a special estimate when the transformation is affine (see~Corollary~6~\cite{stern2013lp}).

\begin{proposition}\label{proposition:pullbackestimate}
    Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
    Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
    Then 
    \begin{align}
        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
        &\leq 
        \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
        .
    \end{align}
    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \dots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
    \begin{align}
        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
        &\leq 
        \sigma_1 \sigma_2 \cdots \sigma_k \cdot 
        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
        .
    \end{align}
\end{proposition}

\begin{remark}
    In three dimensions, 
    the calculus of differential forms is in correspondence with classical vector calculus. 
    This is expressed formally as the commuting diagram 
    \begin{gather*}
    \begin{CD}
        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        @VV{\varpi^{3}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
    \end{CD}
    \cye{\, ,}
    \end{gather*}
    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
    \begin{align*}
     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
     &= 
     \left( u_1, u_2, u_3 \right), 
     \\
     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
     &= 
     \left( u_{23}, - u_{13}, u_{12} \right).   
    \end{align*}
    In two dimensions, 
    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
    To the authors' best knowledge, neither convention is dominant over the other in the literature.
    We summarize the situation in the following commuting diagram: 
    \begin{gather*} 
    \begin{CD}
        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
        \\
        @AA{\varkappa^{0}}A 
        @AA{\varkappa^{1}}A 
        @AA{\varkappa^{2}}A 
        \\
        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
    \end{CD}
    \cye{\,.}
    \end{gather*}
    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism. We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
    The other vertical arrows are the identity. 
    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
\end{remark}

@@

We finally review a few approximation properties. 
Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.

@@

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
\end{proof}

@@

% We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
% We already know the optimal constants for the gradient operator over convex domains,
% and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
% We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$. 
% % 
% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
% We solve this for two special cases:

We now develop bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
Here, we consider two special cases: 
either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
% 
In comparison to their extensive work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our goal are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.

%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.

% \todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
